Natural variation in teosinte at the domestication locus teosinte branched1 (tb1)

### 2014-04-21 manuscript.tex
Edits + Tom's comments on .pdf

To investigate patterns of sequence diversity and linkage disequilibrium (LD) in the \emph{tb1} region, we sequenced two small ($<$1kb) regions upstream of the tb1 ORF in four populations. After alignment and singleton checking we recovered 40 and 48 segregating sites for the 50kb upstream region and the 5' UTR region, respectively. For region 1, Ejutla A has the highest values of haplotype diversity, $\theta_W$, and $\theta_\pi$, while Ejutla B and La Mesa have comparable values of these summary statistics, and San Lorenzo has much lower values. Additionally, Tajima's D is strongly negative in the two Ejutla populations and La Mesa, but is more positive in San Lorenzo (\ref{Table2Diversity}). \jri{can drop theta W from table and text. we show pi and D, which is sufficient. fix caption in table. also add Hopscotch allele frequencies to table or list somewhere -- i think it's useful for comparison of seq stats }
% Table 2 Diversity Statistics
\begin{table}[htbp]
  \centering
  \caption{Add caption}
    \begin{tabular}{lccccc}
%    \toprule
    Population & \# Haplotypes & Hap. Diversity & $\hat\theta_W$    & $\hat\theta_\pi$    & Tajima's D \\
%    \midrule
    \multicolumn{6}{c}{\textit{Seq. region 2 (50kb upstream)}} \\
    \multicolumn{1}{c}{EJUA} & 8     & 0.89394 & 0.01548 & 0.01763 & 0.6231 \\
    \multicolumn{1}{c}{EJUB} & 8     & 0.89394 & 0.01493 & 0.01591 & 0.29504 \\
    \multicolumn{1}{c}{MSA} & 3     & 0.68182 & 0.01111 & 0.01055 & -0.22212 \\
    \multicolumn{1}{c}{SLO} & 4     & 0.74242 & 0.01167 & 0.01413 & 0.93185 \\
    \multicolumn{6}{c}{\textit{Seq.  region 1(5? UTR)}} \\
    \multicolumn{1}{c}{EJUA} & 8     & 0.85897 & 0.00874 & 0.00527 & -1.64955 \\
    \multicolumn{1}{c}{EJUB} & 5     & 0.70909 & 0.00663 & 0.00378 & -1.83123 \\
    \multicolumn{1}{c}{MSA} & 6     & 0.68182 & 0.00646 & 0.00373 & -1.75506 \\
    \multicolumn{1}{c}{SLO} & 3     & 0.31818 & 0.00176 & 0.00137 & -0.72873 \\
 %   \bottomrule
    \end{tabular}
  \label{Table2Diversity}
\end{table}

>>>>

To investigate patterns of sequence diversity and linkage disequilibrium (LD) in the \emph{tb1} region, we sequenced two small ($<$1kb) regions upstream of the tb1 ORF in four populations. After alignment and singleton checking we recovered 40 and 48 segregating sites for the 50kb upstream region and the 5' UTR region, respectively. For region 1, Ejutla A has the highest values of haplotype diversity, and $\theta_\pi$, while Ejutla B and La Mesa have comparable values of these summary statistics, and San Lorenzo has much lower values. Additionally, Tajima's D is strongly negative in the two Ejutla populations and La Mesa, but is more positive in San Lorenzo (\ref{Table2Diversity}). \jri{can drop theta W from table and text. we show pi and D, which is sufficient. fix caption in table. also add Hopscotch allele frequencies to table or list somewhere -- i think it's useful for comparison of seq stats } \lev{the frequencies are in supplemental table 1, do you want them put in this table too, or just me to refer people to supp table 1?}
% Table 2 Diversity Statistics
\begin{table}[htbp]
  \centering
  \caption{Add caption}
    \begin{tabular}{lccccc}
%    \toprule
    Population & \# Haplotypes & Hap. Diversity & $\hat\theta_W$    & $\hat\theta_\pi$    & Tajima's D \\
%    \midrule
    \multicolumn{6}{c}{\textit{Seq. region 2 (50kb upstream)}} \\
    \multicolumn{1}{c}{EJUA} & 8     & 0.89394 & 0.01548 & 0.01763 & 0.6231 \\
    \multicolumn{1}{c}{EJUB} & 8     & 0.89394 & 0.01493 & 0.01591 & 0.29504 \\
    \multicolumn{1}{c}{MSA} & 3     & 0.68182 & 0.01111 & 0.01055 & -0.22212 \\
    \multicolumn{1}{c}{SLO} & 4     & 0.74242 & 0.01167 & 0.01413 & 0.93185 \\
    \multicolumn{6}{c}{\textit{Seq.  region 1(5? UTR)}} \\
    \multicolumn{1}{c}{EJUA} & 8     & 0.85897 & 0.00874 & 0.00527 & -1.64955 \\
    \multicolumn{1}{c}{EJUB} & 5     & 0.70909 & 0.00663 & 0.00378 & -1.83123 \\
    \multicolumn{1}{c}{MSA} & 6     & 0.68182 & 0.00646 & 0.00373 & -1.75506 \\
    \multicolumn{1}{c}{SLO} & 3     & 0.31818 & 0.00176 & 0.00137 & -0.72873 \\
 %   \bottomrule
    \end{tabular}
  \label{Table2Diversity}
\end{table}
